Extended Abstract

### 2021-05-10 paper/paper.tex
Add main references

\begin{abstract}
  The linear \picalc{} is a well-known substructural type system for the \picalc{}:
  it is a common target for the encoding of session-typed languages \todo{cite},
  and it in direct correspondence with classical linear logic \todo{cite}.

@@

We define an untyped but well scoped \picalc{} using type-level de Bruijn \todo{cite} indices \autoref{syntax}.
We define a small expression language within the process syntax to handle composite sum and product types.
On top of the well-scoped syntax we provide the standard linear type-system using context-splits \autoref{type-system}.
The type system is indexed by a typing context that admits unsolved metavariables.
These unsolved metavariables are however well kinded: either types or usage annotations.

@@

A usage annotation $x$, type $t$ or context $\Gamma$ is unrestricted (shared, non-linear) $\tun{\Gamma}$ if it can be split into itself: $\tSplit{\Gamma}{\Gamma}{\Gamma}$ (respectively $x$ and $t$) \todo{cite padovani}.
\todo{typing judgment for variables}

@@

>>>>

\begin{abstract}
  The linear \picalc{} is a well-known substructural type system for the \picalc{}:
  it is a common target for the encoding of session-typed languages \cite{DardhaGS17},
  and it in direct correspondence with classical linear logic \todo{cite}.

@@

We define an untyped but well scoped \picalc{} using type-level de Bruijn \cite{deBruijn72} indices \autoref{syntax}.
We define a small expression language within the process syntax to handle composite sum and product types.
On top of the well-scoped syntax we provide the standard linear type-system using context-splits \autoref{type-system}.
The type system is indexed by a typing context that admits unsolved metavariables.
These unsolved metavariables are however well kinded: either types or usage annotations.

@@

A usage annotation $x$, type $t$ or context $\Gamma$ is unrestricted (shared, non-linear) $\tun{\Gamma}$ if it can be split into itself: $\tSplit{\Gamma}{\Gamma}{\Gamma}$ (respectively $x$ and $t$) \cite{Padovani15}.
\todo{typing judgment for variables}

@@

\cite{McBride03}
